Implications of Differential Evolution for Defect Prediction: Analytics Without Parameter Tuning Considered Harmful

### 2015-03-10 tuningpredictor.tex
add more functions in DE pseudo code
working on pages 1,2

\maketitle
\begin{abstract}

software defect prediction with various 
empirical data sets. Those proposed leaners are always evaluated against the state of the art 
predictors by performing statistical analysis. Undoubtedly, given the bias from data sets and 
accuracy indicators, the newer predictors outperform counterparts in selected experimental 
settings. However,  most of data mining algorithm based predictors (e.g. CART, random 
forest, 
neural networks, SVM) have built-in {\it magic} parameters, like the number of trees in random 
forest algorithm. the impact of internal parameters in those methods have been neglected 
during evaluation. In this paper, we investigate this impact by tuning parameters in defect 
predictors with search-based software engineering algorithm. Specifically, we used differential 
evolution to tune the CART and a new predictor based on WHERE algorithm with local data, 
and then predictors with optimal parameters obtained from tuning process will be applied to 
predict defects. By comparing the performance of predictors with and without tuning process,  
we observe that tuning improves the predictors' performance and predictors woking with 
different data sets need different parameters. Our results also suggest that we should not use 
the predictors of the shelf with their default parameters and tuning should be a processor 
combined with any predictor with built-in parameters.

@@

\begin{raggedleft}
{\em ``The  common misunderstanding about science 
is that scientists seek and find truth. They don't- 
they make and test models.''}\\ -- Neil Gershenfeld

{\em Essentially, all models are wrong, but some are useful."}\\ --George Box

\end{raggedleft}

XXX One consequence of this work is that it is possible to tune a detector such that it exhibits a wide range of performance scores. Given that, the next question becomes ``what performance scores do you want?''. This is an interesting issue since there is no single best answer. XXX

@@

@@

\begin{algorithm}
	\caption{Pesudocode for DE with Early Termination}
	\label{alg:DE}
		\begin{algorithmic}[1]
			\Require $np$, $f$, $cf$, $life$
			\Ensure $S_{best}$
		  \State $Population  \gets $ InitializePopulation($np$)
		  \State $S_{best} \gets $GetBestSolution($Population $)
		  \While{$life > 0$}
			\State $NewGeneration \gets \emptyset$
			\For{$i=0 \to n-1$}
				\State $S_i \gets$ GenNew($Population [i], Population , cf, f)$
				\If {Score($S_i$) >Score($Population [i]$)}
				 	\State $NewGeneration \gets S_i$
				\Else
					\State $NewGeneration \gets Population [i]$
				\EndIf
			\EndFor
			\State $Population  \gets NewGeneration$
			\If{$\neg$ Improve($Population $)}
				\State $life -=1$
			\EndIf
			\State $S_{best} \gets$ GetBestSolution($Population $)
		  \EndWhile
		 \State \Return $S_{best}$
                 \end{algorithmic}            
\end{algorithm}

>>>>

\maketitle
\begin{abstract}
When learning
software defect predictors from static code attributes,   a
very simple optimizer called differential evolution needs can quickly
find  good tunings for that learner.
Such tunings can have a dramatic change to the performance of a learner;
e.g. in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

These results suggest that it is time to change standard practice in
software analytics. Specifically,
it is no longer enough to just run a data miner and present the result
{\em without} first conducting an tuning optimizations study.

@@

%\begin{raggedleft}
%{\em ``The  common misunderstanding about science 
%%is that scientists seek and find truth. They don't- 
%they make and test models.''}\\ -- Neil Gershenfeld

%{\em Essentially, all models are wrong, but some are useful."}\\ --George Box
%%
%\end{raggedleft}

One of the ``black arts'' of data mining is setting the tuning
parameters that control  the choices within that data miner.
Such tunings can have a dramatic change to the performance of a learner;
e.g. in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

Many researchers have applied automatic optimizers to find good tunings.
This paper shows that for at least one software analytics problem
(software defect prediction from static code attributes),   a
very simple optimizer called differential evolution needs only   seconds
to just  few minutes to find good tunings.

These results   challenge much prior work into defect prediction:
\bi 
\item 
Several recent high profile papers have claimed 
that learnerX is better than learnerY for some software analytics task.
For example, a recent IEEE TSE article claimed that the 
CART decision tree learner was far worse than Random Forests for
softwre defect predition. 
We show that tuning can reverse the rankings of data miners such
that, after tuning, the worst untuned learner (CART) can out-perform the supposedly
best learner (Random Forests).
\item
The improvements achieved via differential evolution are too large to discount.
Yet those result show that different attributes are ``best'' for different
data sets and even differnt goals for the tunings. Hence, it is no longer
supportable to use data mining to argue that certain kinds of attributes
are better than others. 
\ei 
Given the simplicity and effectiveness of differential evolution,
and also given the effects this method has on defect prediction, this
paper  motivates  a change to the entire field of software analytics.
It is no longer enough to just run a data miner and present the result
{\em without} first conducting an tuning optimizations study.

\section{Background}
\subsection{Defect Prediction}

This section is our standard introduction to defect prediction~\cite{aa},
plus   some new results from Rahman et al.'s   2014 FSE paper~\cite{rahman14:icse}.

XXXX need our standard table

\input{dm101}

\begin{figure*}[!t]
\renewcommand{\baselinestretch}{0.8}\begin{center}
{\scriptsize
\begin{tabular}{c|l|p{4in}}
amc & average method complexity & e.g. number of JAVA byte codes\\\hline
avg\_cc & average McCabe & average McCabe's cyclomatic complexity seen
in class\\\hline
ca & afferent couplings & how many other classes use the specific
class. \\\hline
cam & cohesion amongst classes & summation of number of different
types of method parameters in every method divided by a multiplication
of number of different method parameter types in whole class and
number of methods. \\\hline
cbm &coupling between methods &  total number of new/redefined methods
to which all the inherited methods are coupled\\\hline
cbo & coupling between objects & increased when the methods of one
class access services of another.\\\hline
ce & efferent couplings & how many other classes is used by the
specific class. \\\hline
dam & data access & ratio of the number of private (protected)
attributes to the total number of attributes\\\hline
dit & depth of inheritance tree &\\\hline
ic & inheritance coupling &  number of parent classes to which a given
class is coupled (includes counts of methods and variables inherited)
\\\hline
lcom & lack of cohesion in methods &number of pairs of methods that do
not share a reference to an instance variable.\\\hline
locm3 & another lack of cohesion measure & if $m,a$ are  the number of
$methods,attributes$
in a class number and $\mu(a)$  is the number of methods accessing an
attribute,\newline
then
$lcom3=((\frac{1}{a} \sum_j^a \mu(a_j)) - m)/ (1-m)$.
\\\hline
loc & lines of code &\\\hline
max\_cc & maximum McCabe & maximum McCabe's cyclomatic complexity seen
in class\\\hline
mfa & functional abstraction & number of methods inherited by a class
plus number of methods accessible by member methods of the
class\\\hline
moa &  aggregation &  count of the number of data declarations (class
fields) whose types are user defined classes\\\hline
noc &  number of children &\\\hline
npm & number of public methods & \\\hline
rfc & response for a class &number of  methods invoked in response to
a message to the object.\\\hline
wmc & weighted methods per class &\\\hline
\rowcolor{lightgray}
defect & defect & Boolean: where defects found in post-release bug-tracking systems.
\end{tabular}
}
\end{center}
\caption{OO measures used in our defect data sets. The last line shows
the dependent attribute (whether any defect is reported to  a
post-release bug-tracking system).}\label{fig:ck}
\end{figure*}

We formulate and present two cost-effectiveness-based
accounting approaches to the comparability of bugginess
identification problem (CBI).
We find no significant differences in the cost-effectiveness
of the DP and the two SBF techniques —
FindBugs and pmd— we could evaluate

\section{Other sutff}
XXX One consequence of this work is that it is possible to tune a detector such that it exhibits a wide range of performance scores. Given that, the next question becomes ``what performance scores do you want?''. This is an interesting issue since there is no single best answer. XXX

@@

Note that we do not claim that differntial evolution is the {\em best} way to
optimize data miners for defect prediction. In this paper, we only show that
differential evolution is {\em simple}, {\em fast} and {\em effective} at that task. As to   finding the best optimizer for defect prediction, that task would require
the input of many researchers (and we hope this paper inspires
much subsequent work into that issue).

@@

\begin{algorithm}
	\caption{Pesudocode for DE with Early Termination}
	\label{alg:DE}
		\begin{algorithmic}[1]
			\Require $np = 10$, $f=0.75$, $cr=0.3$, $life = 5$
			\Ensure $S_{best}$

	      \Function{DE}{$np$, $f$, $cr$, $life$}
		  \State $Population  \gets $ InitializePopulation($np$)
		  \State $S_{best} \gets $GetBestSolution($Population $)
		  \While{$life > 0$}
			\State $NewGeneration \gets \emptyset$
			\For{$i=0 \to np-1$}
				\State $S_i \gets$ GenNew($Population [i], Population , cr, f$)
				\If {Score($S_i$) >Score($Population [i]$)}
				 	\State $NewGeneration$.append($S_i$)
				\Else
					\State $NewGeneration$.append($Population [i]$)
				\EndIf
			\EndFor
			\State $Population  \gets NewGeneration$
			\If{$\neg$ Improve($Population $)}
				\State $life -=1$
			\EndIf
			\State $S_{best} \gets$ GetBestSolution($Population $)
		  \EndWhile
		 \State \Return $S_{best}$
		 \EndFunction
		 \Function{Score}{$Candidate$}
		    \State set tuned parameters according to $Candidate$
		    \State TrainLearner()
		    \State $scores \gets$TestLearner()
		    \State \% scocres = [pd, f, precision]
		    \State $s \gets scores[i] $ 
		    \State \% i determines the goal of tuning
		    \State \Return$s$
		 \EndFunction
		 \Function{GenNew}{$old, pop, cr, f$}
		   \State $a, b, c\gets threeOthers(pop,old)$ 
		   \State \% pick 3 other points from the population
		   \State $newf \gets \emptyset$
		   \For{$i=0 \to np-1$}
		        \If{$cr < random()$}
		          \State $newf$.append($old[i]$)
                \Else
                  \If{typeof(old[i]) == bool}
                    \State $newf$.append(not $old[i]$)
		          \Else
		           \State $newf$.append(trim($i$,($a[i] + f * (b[i] - c[i]$))))
		           \State \%trim() will make new value fall in the range
		          \EndIf
		        \EndIf
		   \EndFor
		 \EndFunction
        \end{algorithmic}            
\end{algorithm}
